Continuous developmental change explains discontinuities in word learning

### 2020-03-20 journal/ms_blind.tex
revisions

\documentclass[english,,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change explains discontinuities in word learning},
            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Continuous developmental change explains discontinuities in word
learning}
    \author{Abdellah Fourtassi\textsuperscript{1}, Sophie Regan\textsuperscript{1},
\& Michael C. Frank\textsuperscript{1}}
    \date{}

\shorttitle{Continuous Development of Word Learning}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University}
\keywords{word learning, cognitive development, computational modeling}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}

\authornote{

@@

Correspondence concerning this article should be addressed to Abdellah
Fourtassi, Postal address. E-mail:
\href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}}

\abstract{
``Cognitive development is often characterized in terms of
discontinuities, but these discontinuities can sometimes be apparent
rather than actual and can arise from continuous developmental change.
To explore this idea, we use as a case study the finding by Stager and
Werker (1997) that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills. Early
explanations proposed that children may not be able to encode subtle
phonetic contrasts when learning novel word meanings, thus suggesting a
discontinuous/stage-like pattern of development. However, later work has
revealed (e.g., through using more precise testing methods) that
children do encode such contrasts, thus favoring a continuous pattern of
development. Here we propose a probabilistic model that represents word
knowledge in a graded fashion and characterizes developmental change as
improvement in the precision of this graded knowledge. Our model
explained previous findings in the literature and provided a new
prediction --- the referents' visual similarity modulates word learning
accuracy. The models' predictions were corroborated by human data we
collected from both preschool children and adults. The broader impact of
this work is to show that computational models, such as ours, can help
us explore the extent to which episodes of cognitive development that
are typically thought of as discontinuities may emerge from simpler,
continuous mechanisms.''

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\section{Introduction}\label{introduction}

@@

To explore this point computationally, we use a case study from word
learning literature. Stager and Werker (1997) first showed that
children's early ability to distinguish similar sounds does not
automatically translate into word learning skills. The authors measured
word learning using an audio-visual habituation Switch task. First,
infants are familiarized with two word-object pairings (e.g., label 1
with object 1 and label 2 with object 2). Second, they are tested using
two types of trials. The control \enquote{same} trial consists of a
correct pairing (e.g., label 1 with object 1) and the \enquote{switch}
trial consists of a wrong pairing (e.g., label 1 with object 2). If
babies have correctly learned the association during the habituation,
they are supposed to be surprised by the \enquote{switch} trial and not
by the \enquote{same} trial. The former should thus result in a greater
looking time compared to the latter (Werker, Cohen, Lloyd, Casasola, \&
Stager, 1998).

@@

The initial discontinuous interpretation has been challenged by
subsequent work. For instance, Yoshida, Fennell, Swingley, and Werker
(2009) investigated whether failure in the Switch task reflects a lack
of sound encoding during \emph{habituation}, or whether it is only due
to the nature of the \emph{testing} method which does not allow learning
below a certain threshold to be detected. They used the same habituation
procedure as Stager and Werker (1997), but instead of comparing the
looking times in \enquote{same} and \enquote{switch} trials, they tested
infants using a two-alternative choice task comparing fixations to
target and distractor objects (Fernald, Perfors, \& Marchman, 2006;
Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987). Using this testing
method, researchers found evidence for learning even in 14-month olds.

@@

In addition to explaining the difference in behavior across the Switch
and the preferential looking tasks, the probabilistic account explains
difference in behavior within the same task. In particular, when the
labels are quite distinct in the perceptual space (\enquote{lif} vs.
\enquote{neem}), the probabilistic distributions do not overlap as much
as in the case of similar-sounding words (Figure \ref{fig:illus}, left).
This fact means that the learners will have less tolerance for the wrong
association, leading to a successful rejection in the Switch task (as
was reported by Stager and Werker (1997) and subsequent studies using
the same paradigm). Further, distinctiveness can be enhanced even for
minimally different sounds when other cues highlight their difference
(Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010;
Thiessen, 2007; Yeung \& Werker, 2009).

@@

\subsection{The current study}\label{the-current-study}

The probabilistic account has been put forward to explain patterns of
learning and development at the qualitative level. However, it is
crucial to have a precise computational instantiation of this account
which would help us 1) test this theoretical hypothesis more directly
and 2) identify the particular parameters that are the locus of
developmental change. One previous study attempted to provide such a
computational instantiation (Hofer \& Levy, 2017). However, this
previous work was designed with the goal of reproducing the results of a
specific study (Pajak et al., 2016) which focused on explaining the
mismatch between speech perception and word learning in adults rather
than on exploring the mechanism of development.

@@

A similar probabilistic structure was used by Lewis and Frank (2013) to
model concept learning, and by Hofer and Levy (2017) to model spoken
word learning. However, the first study assumed that the sounds are
heard unambiguously, and the second assumed the concepts are observed
unambiguously. In our model, we assume that both labels and concepts are
observed with a certain amount of perceptual noise, which we assume, for
simplicity, is captured by a normal distribution:

@@

Finally, we assume there to be one-to-one mappings between concepts and
labels and that observers have successfully learned these mappings
during the exposure phase:

\begin{equation}
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{otherwise  }
\end{cases}
\end{equation}

\subsection{Inference}\label{inference}

@@

We use the model to predict word learning in a task similar to the one
introduced by Stager and Werker (1997). We used a modified version of
the task where the testing method consists in a two-alternative
forced-choice (Yoshida et al., 2009). In this task, participants are
first exposed to two different word-object pairings (e.g., \enquote{lif}
- object 1, \enquote{neem} - object 2). The word-object associations are
introduced sequentially. After this exposure phase, participants perform
a series of test trials. In each of these trials, one of the two sounds
is uttered (e.g., \enquote{lif}) and participants choose the
corresponding object from the two alternatives. An overview of the task
is shown in Figure \ref{fig:task}.

\subsubsection{Model 1}\label{model-1}

From the general expression \ref{eq:general}, we derive three exact
analytical solutions instantiating different learning assumptions.
Recall from expressions \ref{eq:object} and \ref{eq:sound} that
\(P(o|C)\) and \(P(s|L)\) have parameters \(\sigma_C\) and \(\sigma_L\),
respectively, that control perceptual uncertainty. The first solution is
derived by assuming that the labels are recovered from sounds with a
certain level of uncertainty \(\sigma_L > 0\), but that concepts are
unambiguously recovered from the observed objects, i.e.,
\(\sigma_C \rightarrow 0\). This assumption has been made --- whether
implicitly or explicitly --- by most previous work in this line of
research. For example, in Stager and Werker (1997), the objects were
quite dissimilar. Thus, the assumption that they were easily
discriminated by infants seems relatively well justified. One important
implication of this assumption is that only the similarity of word
sounds modulates success in word learning, not the similarity of the
referents (as long as these referents are differentiated perceptually).
This assumption yields the following probability function:

\begin{equation} \label{eq:model1}
P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
\end{equation}

where \(\Delta s = s_2-s_1\).

\subsubsection{Model 2}\label{model-2}

@@

\begin{equation} \label{eq:model2}
P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
\end{equation}

\subsubsection{Model 3}\label{model-3}

@@

\begin{equation} \label{eq:model3}
P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
\end{equation}

In order to understand the predictions of the models (especially the
more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation}
show simulations of the accuracy \(P(o_T|s)\) as a function of the
distinctiveness parameters (\(\Delta s\) and \(\Delta o\)) and the
uncertainty parameters \(\sigma_L\) and \(\sigma_C\).

\begin{figure}[htbp]
\centering
\includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate
responses in the testing phase as a function of stimuli distinctiveness
\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
(For simplicity, we use model 2, which assumes that
\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
\end{figure}

@@

\subsubsection{Stimuli and similarity
rating}\label{stimuli-and-similarity-rating}

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
generated three kinds of nonsense word pairs which varied in their
degree of perceptual similarity to English speakers: 1) \emph{different}
pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2)
\emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and
\enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs:
\enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and
\enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).

@@

In order to validate and quantify our similarity scales, we ran a
separate survey on Amazon Mechanical Turk where we asked \(N=20\) adults
participants to evaluate the similarity of each sound and object pair on
a 7-point scale. Data are shown in Figure \ref{fig:stim} where we scaled
responses within the range {[}0,1{]} for each stimulus group. We used
these data in all models as an empirical measurement of the perceptual
distance between the sound pairs and the object pairs. The use of
empirical measurement allows us to eliminate \(\Delta s\) and
\(\Delta s\) as free parameters (see Frank and Goodman (2012) and Xu and
Tenenbaum (2007) for a similar strategy).

\subsubsection{Design}\label{design}

@@

\caption{Distances for both sound and object pairs from an adult norming study. Data represent Likert values normalized to [0,1] interval. Error bars represent 95\% confidence intervals.}\label{fig:stim}
\end{figure}

@@

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (about 800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing trial.

@@

\subsection{Results}\label{results}

@@

For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{}
0.001), and this finding confirms the new prediction of our model,
according to which, object distance also modulates success in word
learning. Note, in particular, that increasing the visual similarity of
the objects makes children succeed in learning the similar-sounding
words. Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\)
\textless{} 0.001), showing that overall performance improves with age.
The full output of the regression model is shown in Table 2.

>>>>

\documentclass[english,,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change explains discontinuities in word learning},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

  \title{Continuous developmental change explains discontinuities in word learning}
    \author{true \\ true \\ true}
    \date{}

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Continuous Development of Word Learning}
\author{Abdellah Fourtassi\textsuperscript{1}, Sophie Regan\textsuperscript{1}, \& Michael C. Frank\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University}
\authornote{

@@

Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: afourtas@stanford.edu}
\keywords{word learning, cognitive development, computational modeling}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}
\usepackage{xcolor}

\abstract{
``Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change. To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills. Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development. However, later work has revealed (e.g., through using more precise testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development. Here we propose a probabilistic model that represents word knowledge in a graded fashion and characterizes developmental change as improvement in the precision of this graded knowledge. Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy. The models' predictions were corroborated by human data we collected from both preschool children and adults. The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.''
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

To explore this point computationally, we use a case study from word learning literature. Stager \& Werker (1997) first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills. The authors measured word learning using an audio-visual habituation Switch task. First, infants are familiarized with two word-object pairings (e.g., label 1 with object 1 and label 2 with object 2). Second, they are tested using two types of trials. The control \enquote{same} trial consists of a correct pairing (e.g., label 1 with object 1) and the \enquote{switch} trial consists of a wrong pairing (e.g., label 1 with object 2). If babies have correctly learned the association during the habituation, they are supposed to be surprised by the \enquote{switch} trial and not by the \enquote{same} trial. The former should thus result in a greater looking time compared to the latter (Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).

@@

The initial discontinuous interpretation has been challenged by subsequent work. For instance, Yoshida, Fennell, Swingley, \& Werker (2009) investigated whether failure in the Switch task reflects a lack of sound encoding during \emph{habituation}, or whether it is only due to the nature of the \emph{testing} method which does not allow learning below a certain threshold to be detected. They used the same habituation procedure as Stager \& Werker (1997), but instead of comparing the looking times in \enquote{same} and \enquote{switch} trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects (Fernald, Perfors, \& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987). Using this testing method, researchers found evidence for learning even in 14-month olds.

@@

In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains difference in behavior within the same task. In particular, when the labels are quite distinct in the perceptual space (\enquote{lif} vs. \enquote{neem}), the probabilistic distributions do not overlap as much as in the case of similar-sounding words (Figure \ref{fig:illus}, left). This fact means that the learners will have less tolerance for the wrong association, leading to a successful rejection in the Switch task (as was reported by Stager \& Werker (1997) and subsequent studies using the same paradigm). Further, distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference (Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010; Thiessen, 2007; Yeung \& Werker, 2009).

@@

\hypertarget{the-current-study}{%
\subsection{The current study}\label{the-current-study}}

The probabilistic account was used before to explain patterns of learning and development at the qualitative level (e.g., Swingley, 2007). However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change. One previous study attempted to provide such a computational instantiation (Hofer \& Levy, 2017). However, this previous work was designed with the goal of reproducing the results of a specific study (Pajak et al., 2016) which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.

@@

A similar probabilistic structure was used by Lewis \& Frank (2013) to model concept learning, and by Hofer \& Levy (2017) to model spoken word learning. However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously. In our model, we assume that both labels and concepts are categories with possibly overlapping distributions. In other words, we allow the model to account for the --- more realistic --- possibility that an instances of a given categories (e.g.,\enquote{bin}) can be mistaken for an instance of a neighboring category (e.g., \enquote{din}), albeit with a smaller probability. We assume, for simplicity, that this probability is captured by a normal distribution\footnote{\textcolor{red}{We used a normal distribution to simplify the mathematical derivations. This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}}:

@@

Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
\begin{equation}\label{eq:mapping}
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{otherwise  }
\end{cases}
\end{equation}

\hypertarget{inference}{%
\subsection{Inference}\label{inference}}

@@

We use the model to predict word learning in a task similar to the one introduced by Stager \& Werker (1997). We used a modified version of the task where the testing method consists in a two-alternative forced-choice (Yoshida et al., 2009). In this task, participants are first exposed to two different word-object pairings (e.g., \enquote{lif} - object 1, \enquote{neem} - object 2). The word-object associations are introduced sequentially. After this exposure phase, participants perform a series of test trials. In each of these trials, one of the two sounds is uttered (e.g., \enquote{lif}) and participants choose the corresponding object from the two alternatives. An overview of the task is shown in Figure \ref{fig:task}.

From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.

\hypertarget{model-1}{%
\subsubsection{Model 1}\label{model-1}}

Recall from expressions \ref{eq:object} and \ref{eq:sound} that \(P(o|C)\) and \(P(s|L)\) have parameters \(\sigma_C\) and \(\sigma_L\), respectively, that control for uncertainty. The first solution/model is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty \(\sigma_L > 0\), but that concepts are unambiguously recovered from the observed objects, i.e., \(\sigma_C \rightarrow 0\). This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research. For example, in Stager \& Werker (1997), the objects were quite dissimilar. Thus, the assumption that they were easily discriminated by infants seems relatively well justified. One important implication of this assumption is that only the similarity of word sounds modulates performance in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).

This assumption yields the following probability function of choosing the correct object \(o_i\) given the correspondding label instance \(s_i\), where \(i \in \{1,2\}\) (see the Appendix for the full mathematical derivation):

\begin{equation} \label{eq:model1}
P(o_i|s_i)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
\end{equation}

where \(\Delta s = s_2-s_1\) is the perceptual sound distance between the pair of sounds that we refer to as \(s_1\) and \(s_2\). These distances were measured empirically as shown in Figure \ref{fig:stim}.

\hypertarget{model-2}{%
\subsubsection{Model 2}\label{model-2}}

@@

\begin{equation} \label{eq:model2}
P(o_i|s_i)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
\end{equation}

\hypertarget{model-3}{%
\subsubsection{Model 3}\label{model-3}}

@@

\begin{equation} \label{eq:model3}
P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
\end{equation}

In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy \(P(o_i|s_i)\) as a function of the distinctiveness parameters (\(\Delta s\) and \(\Delta o\)) and the uncertainty parameters \(\sigma_L\) and \(\sigma_C\).

\begin{figure}
\centering
\includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness \(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\) (For simplicity, we use model 2, which assumes that \(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
\end{figure}

@@

\hypertarget{stimuli-and-similarity-rating}{%
\subsubsection{Stimuli and similarity rating}\label{stimuli-and-similarity-rating}}

The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) \emph{different} pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2) \emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and \enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs\footnote{For the intermediate/similar pairs, we made the choice of using a VCV (Vowel-Consonant-Vowel) structure in order to emphasize the phonemic difference in the minimal pairs, especially for the non-native contrasts. However, as one reviwer rightfully pointed out to us, this structure could influence word leaning performance since it is not common in English. Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand. However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic). For the simialr pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults. In this respect, we took inspiration from the work of Pajak et al. (2016). We refer the reader to that paper for a lengthy discussion of the literature on (and implications for) L2 phoneme perception.

@@

In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked \(N=20\) adults participants to evaluate the similarity of each sound and object pair on a 7-point scale. Data are shown in Figure \ref{fig:stim} where we scaled responses within the range {[}0,1{]} for each stimulus group. We used these data in all models as an empirical measurement of the perceptual distance between the sound pairs and the object pairs. The use of empirical measurement allows us to eliminate \(\Delta s\) and \(\Delta s\) as free parameters (see Frank \& Goodman (2012) and Xu \& Tenenbaum (2007) for a similar strategy).

\hypertarget{design}{%
\subsubsection{Design}\label{design}}

@@

\caption{Distances for sound and object pairs ($\Delta s$ and $\Delta o$, respectively) from an adult norming study. Data represent Likert values normalized to [0,1] interval. Error bars represent 95\% confidence intervals.}\label{fig:stim}
\end{figure}

@@

In the exposure trials, participants saw two objects associated with their corresponding sounds. We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound. The second sound-object association followed on the other side of the screen after 500ms. For both objects, visual stimuli were present for the duration of the sound clip (about 800ms). During this phase, participant were asked to pay attention and try yo lean the words. In the testing trials, participants saw both objects simultaneously and heard only one sound. They completed the trial by selecting which of the two objects corresponded to the sound. The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs.~right) of the two pictures on each testing trial. The online experiment can be viewed at XXX

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{} 0.001), and this finding confirms the new prediction of our model, according to which, object distance also modulates performance in word learning. Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\) \textless{} 0.001), showing that overall performance improves with age. The full output of the regression model is shown in Table 2.

In particular, while children were not different form chance in the most difficult condition when both the sounds and objects are similar . Note, however, the differe that the difference between the these two conditions was not itself
